### 2019-05-21 thesis.tex
plasma definition
Not ready yet.

A plasma is an ionized gas in which the charged particle population is sufficiently
large so the forces of electric and magnetic nature, generated by the charges and
their movement, overcome the influence of the collisions between neutral particles,
that dominate the kinetics of neutral gases, on the overall dynamics of the system.

When it comes to the plasma kinetic theory, processes involving waves
and kinetic instabilities, the so-called \emph{collective processes},
are almost exclusively associated with situations in which the effects
of collisional dissipation can be neglected, what happens when the
studied phenomenon evolves in a much shorter time-scale than the
collisional relaxation time of the plasma in question \cite{akhi1967}.
In such cases, the plasma dynamics may be described by the Vlasov-Maxwell
system, a complex set of coupled equations whose solution invariably will
depend on some degree of approximation. In the presence of small
amplitude oscillations in a fully ionized plasma, we can make use
of perturbation theory in order to solve such complicated system
\cite{klimo}. From this method, one may obtain simpler approximations
like the linear theory and the quasilinear formalism, and also
more complex formulations, like the weak turbulence theory, which
takes into account low-order nonlinearities on the plasma dynamics.

@@

\chapter{Theoretical framework}
\label{cha:theo-fram}

>>>>

% A plasma is an ionized gas in which the charged particle population is sufficiently
% large so the forces of electric and magnetic nature, generated by the charges and
% their movement, overcome the influence of the collisions between neutral particles,
% that dominate the kinetics of neutral gases, on the overall dynamics of the system.
Plasma physics is the area

In the context of plasma kinetic theory, processes involving waves
and kinetic instabilities, the so-called \emph{collective processes},
are almost exclusively associated with situations in which the effects
of collisional dissipation can be neglected, what happens when the
studied phenomenon evolves in a much shorter time-scale than the
collisional relaxation time of the plasma in question \cite{akhi1967}.
In such cases, the plasma dynamics may be described by the Vlasov-Maxwell
system, a complex set of coupled equations whose solution invariably will
depend on some degree of approximation. In the presence of small
amplitude oscillations in a fully ionized plasma, we can make use
of perturbation theory in order to solve such complicated system
\cite{klimo}. From this method, one may obtain simpler approximations
like the linear theory and the quasilinear formalism, and also
more complex formulations, like the weak turbulence theory, which
takes into account low-order nonlinearities on the plasma dynamics.

@@

\chapter{Theoretical framework}
\label{cha:theo-fram}
Let us consider a given set of atoms or molecules, which is composed of
positively and negatively charged particles, and also neutral components.
One can say, correctly, that such a system is an ionized gas, because of
the presence of charged particles in its composition. However, what can
be said about the dominant dynamics of the ionized gas, since neutral and
charged particles have quite a distinct behavior? Assuming the gravitational
force is negligible, the neutral particles will move freely in the medium
until one collides with another \cite{chen}. Thus, the interaction between
the neutral components is characterized as short-ranged, since it relies
only on binary collisions.
